---
title: "Get Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package is designed to retrieve raw data from the Devaluation study from two sources -- questionnaires administered via [Qualtrics](https://www.qualtrics.com/) and a host of measures collected via [Redcap](https://www.project-redcap.org/), including outcome measures such as body mass, BMI, and hip-waist ratio. 

These data are collected from participants across 6 sessions: 

|Session   |Study timepoint |
|:---------|:------------------ |
|Session 0 | Initial visit      |
|Session 1 | Pre-intervention   |
|Session 2 | Post-intervention  | 
|Session 3 | 3-month follow-up  |
|Session 4 | 6-month follow-up  | 
|Session 5 | 12-month follow-up | 

**Note.** Data are currently not publicly available, as data collection is ongoing, so the examples included here demonstrate code usage only and do not include output.

## API credentials file

To access data, you will need a credentials file, saved in .csv format, that contains valid API tokens for Qualtrics and Redcap, along with the proper UO-specific base URL for each platform. (The example shown here does not contain valid tokens.)

```{r message=FALSE}
library(readr)
read_csv("credentials.csv")
```

## Qualtrics

To access survey data from Qualtrics, first register your Qualtrics credentials in your current R session by passing the path to where your credentials file is saved to `register_qualtrics_credentials()`.

```{r eval=FALSE}
library(devaluation)
register_qualtrics_credentials(path_to_creds = "credentials.csv")
```

Once your credentials are registered, you can use `get_survey_info()` to obtain metadata about Qualtrics surveys, including the date each survey was last modified and the number of observations collected.

```{r eval=FALSE}
get_survey_info()
```

To include the raw data along with survey metadata, set `append_raw_data = TRUE`. This returns a nested tibble in which raw data are saved as a list column.

```{r eval=FALSE}
get_survey_info(append_raw_data = TRUE)
```

You can also retrieve raw survey data for a given session with `get_survey_responses_raw()`.

```{r eval=FALSE}
get_survey_responses_raw(session = 1)
```

## Redcap

Get raw Redcap data with `get_redcap_raw()`. Rather than register your Redcap credentials in your session, simply feed this function the path to your credentials file with the `path_to_creds` argument.

```{r eval=FALSE}
get_redcap_raw(path_to_creds = "credentials.csv")
```

By default, identifiable information is excluded when retrieving raw Redcap data. To include identifiable variables, you must set `identifiable = TRUE`.

```{r eval=FALSE}
get_redcap_raw(path_to_creds = "credentials.csv", identifiable = TRUE)
```
